Windowed least-squares model reduction for dynamical systems

### 2019-10-18 main.tex

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) approach for model-reduction
	of dynamical systems. The proposed approach sequentially minimizes the
	time-continuous full-order-model residual within a low-dimensional space--time trial
	subspace over time windows. The approach comprises a generalization 
of existing model reduction approaches, as particular instances of
  the methodology recover Galerkin,
	least-squares Petrov--Galerkin (LSPG), and space–time LSPG projection. In
	addition, the approach
	addresses key deficiencies in existing model-reduction
	techniques, e.g., the dependence of LSPG and space--time LSPG projection on the
	time discretization and the exponential growth in time exhibited by \textit{a posteriori}
	error bounds for both Galerkin and LSPG projection.  We consider two types of
	space--time trial
	subspaces within the proposed approach: one that reduces only the spatial dimension of the full-order model, and one that reduces both the spatial and temporal dimensions of the full-order model. For each type of trial
	subspace, we consider two different solution techniques: direct (i.e.,
	discretize-then-optimize) and indirect (i.e., optimize-then-discretize).
	Numerical experiments conducted using trial subspaces characterized by spatial
	dimension reduction demonstrate that the \methodAcronym\
	approach can yield more accurate solutions with lower space--time residuals than
	Galerkin and LSPG projection.

>>>>

\address[a]{Sandia National Laboratories,  Livermore, CA}
\begin{abstract}
This work proposes a \methodNameLower\ (\methodAcronym) approach for model-reduction
	of dynamical systems. The proposed approach sequentially minimizes the
	time-continuous full-order-model residual within a low-dimensional space--time trial
	subspace over time windows. The approach comprises a generalization 
of existing model reduction approaches, as particular instances of
  the methodology recover Galerkin,
	least-squares Petrov--Galerkin (LSPG), and space–time LSPG projection. In
	addition, the approach
	addresses key deficiencies in existing model-reduction
	techniques, e.g., the dependence of LSPG and space--time LSPG projection on the
	time discretization and the exponential growth in time exhibited by \textit{a posteriori}
	error bounds for both Galerkin and LSPG projection.  We consider two types of
	space--time trial
	subspaces within the proposed approach: one that reduces only the spatial dimension of the full-order model, and one that reduces both the spatial and temporal dimensions of the full-order model. For each type of trial
	subspace, we consider two different solution techniques: direct (i.e.,
	discretize then optimize) and indirect (i.e., optimize then discretize).
	Numerical experiments conducted using trial subspaces characterized by spatial
	dimension reduction demonstrate that the \methodAcronym\
	approach can yield more accurate solutions with lower space--time residuals than
	Galerkin and LSPG projection.
